Fast Hyper-Parameter Selection for Graph Kernels via Subsampling and Multiple Kernel Learning

### 2016-11-24 paper.tex
Modified dataset description

\section{Experimental Assessment}
We conducted our experiments on five real-world datasets:
AIDS~\cite{Weislow1989a}, CAS\footnote{http://cheminformatics.org/datasets/bursi/},
CPDB~\cite{Helma2004a}, NCI1~\cite{Wale2006} and GDD~\cite{dobson2003}.
The first four datasets contain chemical particles encoded in graph form, while the latter encodes proteins.
All the nodes are labelled and there are no self loops.
The AIDS dataset contains 1503 chemical compounds, labelled according to
their antiviral activity; CAS and CPDB store 4337 and 684 mutagenic
compounds respectively; NCI1 consists of 4110 chemical compounds screened for activity against 
non-small lung cancer cells; GDD is composed of 1178 X-ray crystal structures of
proteins.

>>>>

\section{Experimental Assessment}
We conducted our experiments on five real-world datasets (see \cite{DaSanMartino2016} for a more detailed description).
%AIDS~\cite{Weislow1989a}, CAS\footnote{http://cheminformatics.org/datasets/bursi/},
%CPDB~\cite{Helma2004a}, NCI1~\cite{Wale2006} and GDD~\cite{dobson2003}.
%The first four datasets contain chemical particles encoded in graph form, while the latter encodes proteins.
All the nodes are labelled and there are no self loops.
The AIDS dataset contains 1503 chemical compounds (encoded in graph form), labelled according to
their antiviral activity; CAS and CPDB store 4337 and 684 mutagenic
compounds respectively; NCI1 consists of 4110 chemical compounds screened for activity against 
non-small lung cancer cells; GDD is composed of 1178 X-ray crystal structures of
proteins.
All the datsets represent binary classification problems.
